On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-05-31 Manuscript/manuscript.tex
minor comments/edits

\bigskip\noindent\sc{Keywords}:
False Start, Hurdles, Reaction Time, Seiko

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{2019vs2022BarGraph}
  \caption{The reaction times from 2019 and 2022 World Track and Field
  Championship. ``H'', ``S'', and``F'' refer to the heats, semifinals, and finals
  respectively.}
  \label{fig:2019vs2022Graph}
\end{figure}
\of{I included this here for now, but feel free to change the location.  I will
add references to it and explanation of it along with some descriptive statistics about
the size and mean/median,std dev, size of the data.}

@@

\subsection{GLMM}\label{sec:glmm}
Based on an exploratory analysis using the GLMM model for the reaction times
from the World Championships, the final model we chose was a gamma mixed-effect 
model. As suggested by the log-likelihood and the Akaike Information
Criterion (AIC), the normal error model on the log-scale was found to be
much inferior to the gamma model which better captures the skewness of the
data. A random effect for the venue or year was also found to be necessary, 
which makes intuitive sense given the discussion in Section~\ref{sec:dataworld}. 
Let $Y_{ij}$ be the reaction time of observation~$j$ in year~$i$.
\eds{we know that many of the athletes compete in multiple world championships,
  how is this athlete clustering being accounted for here?}
\jy{We could add an athlete random effect too, if the players are identified in the data.}
Conditional on a venue effect $z_i$ of year~i,  $Y_{ij}$ is modeled by 
gamma distribution. In the classic generalized linear model (GLM) sense,
$Y_{ij}$ has conditional mean
\[
g\{E(Y_{ij} | z_i)\} = \alpha + z_i,
\]
and dispersion parameter $\phi$, where $g$ is a known link function and
$z_i$ is a normally distributed random effect with mean zero and
variance~$\sigma^2$. Although \citet{lo2015idlink} suggested that the gamma 
family with an identity link works well for reaction time data, the logarithm 
link function worked better for our data and additionally ensures the positivity
of the conditional mean. The gamma mixed-effect model can be fit with the 
\texttt{glmer()} function in R package \texttt{lme4} \citep{lme4}.

@@

Although it is possible that one athlete reacting faster could lead to others reacting
similarly, this does not make much practical sense as the difference between
heats that had fast and slow reaction times are all within 0.12 seconds of each
other. 
\eds{Did you try it and find that the effect was not needed?  If yes,
I would include that here.  That argument 
would be more compelling for its non-use than its difficulty in interpretation.}
\of{We found that including the race effect resulted in the venue effect not
being significant, and thus Prof Yan suggested that we don't include it.  I am
wondering if this is even worth mentioning? Prof Yan, what do you think?}

@@

\jy{motivate first; describe the data (what are the grouping variables in the
  two data sets? use one paragraph for each.}
\of{Shouldnt describing the grouping variables go more in the data or methods 
section?  Currently, there is some writing about this but it is commented out. It
can be found in section 3.2}

>>>>

\bigskip\noindent{\sc Keywords}:
False Start, Hurdles, Reaction Time, Seiko

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{2019vs2022BarGraph}
  \caption{The reaction times from 2019 and 2022 World Track and Field
  Championship. ``H'', ``S'', and``F'' refer to the heats, semifinals, and finals
  respectively.}
  \label{fig:2019vs2022Graph}
\end{figure}
\of{I included this here for now, but feel free to change the location.  I will
add references to it and explanation of it along with some descriptive statistics about
the size and mean/median,std dev, size of the data.}
\jy{Show dot plots which would give the distribution; without uncertainty
  measure, the mean does not tell much.}

@@

\subsection{GLMM}\label{sec:glmm}
Based on an exploratory analysis using the GLMM model for the reaction times
from the World Championships, the final model we chose was a gamma mixed-effect 
model. As suggested by the log-likelihood and the Akaike Information
Criterion (AIC), the normal error model on the log-scale was found to be
much inferior to the gamma model which better captures the skewness of the
data. A random effect for the venue or year was also found to be necessary, 
which makes intuitive sense given the discussion in Section~\ref{sec:dataworld}. 
Let $Y_{ij}$ be the reaction time of observation~$j$ in year~$i$.
\eds{we know that many of the athletes compete in multiple world championships,
  how is this athlete clustering being accounted for here?}
\jy{We could add an athlete random effect too, if the players are identified in
  the data.}
\jy{Owen, do we have athlete id in the data?}
Conditional on a venue effect $z_i$ of year~i,  $Y_{ij}$ is modeled by 
gamma distribution. In the classic generalized linear model (GLM) sense,
$Y_{ij}$ has conditional mean
\[
g\{E(Y_{ij} | z_i)\} = \alpha + z_i,
\]
and dispersion parameter $\phi$, where $g$ is a known link function and
$z_i$ is a normally distributed random effect with mean zero and
variance~$\sigma^2$. Although \citet{lo2015idlink} suggested that the gamma 
family with an identity link works well for reaction time data, the logarithm 
link function worked better for our data and additionally ensures the positivity
of the conditional mean. The gamma mixed-effect model can be fit with the 
\texttt{glmer()} function in R package \texttt{lme4} \citep{lme4}.

@@

Although it is possible that one athlete reacting faster could lead to others reacting
similarly, this does not make much practical sense as the difference between
heats that had fast and slow reaction times are all within 0.12 seconds of each
other. 
\eds{Did you try it and find that the effect was not needed?  If yes,
I would include that here.  That argument 
would be more compelling for its non-use than its difficulty in interpretation.}
\of{We found that including the race effect resulted in the venue effect not
being significant, and thus Prof Yan suggested that we don't include it.  I am
wondering if this is even worth mentioning? Prof Yan, what do you think?} 
\jy{We can revisit the results. It is not surprising that venue effect is no
  longer significant after the batch effect was included. We could do the same
  analysis with the batch-random-effect model.}

@@

\jy{Remind the readers what the analysis was about: two-group comparison with
  group being ....}
